comgen-outline

### 2017-12-16 paper/comgen-paper.Rmd
refactor fig1, start to remake gen priors task fig, some edits to causals

```{r libraries, cache = F}
library(papaja)
library(formatR)
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
# library(dplyr)
library(data.table)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
library(gridExtra)
library(lme4)
library(knitr)
library(kableExtra)
library(cowplot)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
logmeanexp <- function(x){
  x.num <- as.numeric(x)
  xstar = max(x.num)
  return(xstar + log(mean(exp(x.num - xstar))))
}

@@

```{r simluationsModel, eval = T, cache = T}
l0.model <- '
var probability = function(Dist, x) {
    return Math.exp(Dist.score(x));
}
var targetUtterance = "generic";

var utterancePrior = Infer({model: function(){
  return uniformDraw([targetUtterance,"silence"])
}});

var thetaPrior = Infer({model: function(){
 return uniformDraw([
   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
 ])}
});

var bins = [
  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
];

@@

var statePrior = Infer({model: function(){
  var component = flip(mixture);
  return component ?
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta(priorParams), b) + Number.EPSILON
      }, bins )
    }) :
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
      }, bins )
    })
}});

var listener0 = cache(function(utterance) {
  Infer({model: function(){
    var state = sample(statePrior)
    var state_prior = sample(statePrior)
    var theta = utterance == "generic" ? sample(thetaPrior) : -99
    condition(meaning(utterance, state, theta))
    return {
      state_Posterior: state, 
      state_Prior: state_prior
  }
 }})}, 10000)

var continuousListener0 = function(utterance) {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
//     var state = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
//     var state_prior = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
//    var theta = uniform(0,1)
    factor(
    (utterance == "generic") ? 
      Math.log(state) : 
    (state > 0.017) ? 0 : -Infinity
    )
    return {
      state_Posterior: state, 
      state_Prior: state_prior
  }
 }, method: "rejection", samples: 20000, burn:5000, verbose: T})}

//var out = {generic: listener0("generic"), some: listener0("some")}
//out
continuousListener0(data.utt[0])
'

priorNames <- c(
  "doesntEatPeople", #"uniformRare", 
  "isFemale", 
  "laysEggs", 
  #"eatsFood", 
  "barks",
  "carriesMalaria",
  "hasSpots"
 # "areSick"
  )
priorShapes <- list(
  isFemale =  list(params = data.frame(a = 10, b = 10), mix = 1), 
  laysEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.4), 
  doesntEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1), 
  barks =  list(params = data.frame(a = 5, b = 1), mix = 0.4), 
  hasSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7), 
  carriesMalaria =  list(params = data.frame(a = 2, b = 10), mix = 0.4)
)

all.simulations <- data.frame()
for (p in priorNames){
  for (u in c("generic")){

    inputData = list(prior = priorShapes[[p]], utt = u)
    l0.rs <- webppl(l0.model, data = inputData, data_var = "data")

    # all.simulations <- bind_rows(all.simulations,
    #                         bind_rows(
    #                           data.frame(l0.rs$generic) %>%
    #                             gather(key, val, -probs) %>%
    #                              group_by(key, val) %>%
    #                              summarize(prob = sum(probs)) %>%
    #                             ungroup() %>%
    #                               mutate(key = gsub("support.", "", key)) %>%
    #                              separate(key, into = c("Parameter","Distribution")) %>%
    #                               mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution)),
    #                           data.frame(l0.rs$some) %>%
    #                             gather(key, val, -probs) %>%
    #                             group_by(key, val) %>%
    #                             summarize(prob = sum(probs)) %>%
    #                             ungroup() %>%
    #                             mutate(key = gsub("support.", "", key)) %>%
    #                             separate(key, into = c("Parameter","Distribution")) %>%
    #                             mutate(Distribution = gsub("Posterior", "Posterior_0", Distribution)) %>%
    #                             filter(Distribution != "Prior"),
    #                           data.frame(l0.rs$most) %>%
    #                             gather(key, val, -probs) %>%
    #                             group_by(key, val) %>%
    #                             summarize(prob = sum(probs)) %>%
    #                             ungroup() %>%
    #                             mutate(key = gsub("support.", "", key)) %>%
    #                             separate(key, into = c("Parameter","Distribution")) %>%
    #                             mutate(Distribution = gsub("Posterior", "Posterior_05", Distribution)) %>%
    #                             filter(Distribution != "Prior")
    #                         ) %>%
    #                           mutate(PriorShape = p)
    # )
      all.simulations <- bind_rows(all.simulations,
                                   l0.rs %>%
                                  separate(Parameter, into = c("Parameter","Distribution")) %>%
                                  mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution))
                                  %>%
                              mutate(PriorShape = p, utterance = u)
    )
  }
  #print(p)
}
```
```{r simluationEndorsementModel, eval = T, cache = T}
s1.model <- '
var probability = function(Dist, x) {
    return Math.exp(Dist.score(x));
}
var targetUtterance = "generic";

var utterancePrior = Infer({model: function(){
  return uniformDraw([targetUtterance,"silence"])
}});

var thetaPrior = Infer({model: function(){
 return uniformDraw([
   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
 ])}
});

var bins = [
  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
];

var mixture = data.mix[0];
var priorParams = data.params[0];

var statePrior = Infer({model: function(){
  var component = flip(mixture);
  return component ?
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta(priorParams), b) + Number.EPSILON
      }, bins )
    }) :
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
      }, bins )
    })
}});

var continuousListener0 = function(utterance) {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    factor(
    (utterance == "generic") ? 
      Math.log(state) : 
    (state > 0.017) ? 0 : -Infinity
    )
    return {
      state_Posterior: state, 
      state_Prior: state_prior
  }
 }, method: "rejection", samples: 20000, burn:5000, verbose: T})}

var listener0 = cache(function(utterance) {
  Infer({model: function(){
    var state = sample(statePrior)
    var state_prior = sample(statePrior)
    var theta = utterance == "generic" ? sample(thetaPrior) : -99
    condition(meaning(utterance, state, theta))
    return {
      state_Posterior: state, 
      state_Prior: state_prior
  }
 }})}, 10000)
var alpha = 2

var endorser = function(featureProb){
  Infer({model: function(){
    var endorsement = sample(utterancePrior)
    var L0 = marginalize(listener0(endorsement), "state_Posterior")
    factor(alpha * L0.score(featureProb))
    return endorsement
  }})
}

probability(endorser(data.featureProb[0]), "generic")
'

exampleGenerics <- c(
  "sharksDontEatPeople",
  "robinsAreFemale", 
  "robinsLayEggs", 
  "kangaroosHaveSpots",
  "dogsBark",
  "mosquitosCarryMalaria"
  )
exampleParameters <- list(
  robinsAreFemale =  list(params = data.frame(a = 10, b = 10), mix = 1, featureProb = 0.5), 
  robinsLayEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.2, featureProb = 0.5), 
  sharksDontEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1, featureProb = 0.8), 
  dogsBark =  list(params = data.frame(a = 5, b = 1), mix = 0.4, featureProb = 0.9), 
  kangaroosHaveSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7, featureProb = 0.1), 
  mosquitosCarryMalaria =  list(params = data.frame(a = 1, b = 30), mix = 0.1, featureProb = 0.1)
)

@@

    s1.rs <- webppl(s1.model, data = exampleParameters[[p]], data_var = "data")
    s1.simulations <- bind_rows(s1.simulations,
                                   data.frame(example = p, endorsement = s1.rs, featureProb = exampleParameters[[p]]["featureProb"] ))

@@

```{r}
s1.simulations.relabeled <- s1.simulations %>%
  mutate(example = factor(example, 
                          levels = c("dogsBark", "kangaroosHaveSpots", "sharksDontEatPeople", "robinsLayEggs", "robinsAreFemale", "mosquitosCarryMalaria"),
                            labels = c("Dogs bark", "Kangaroos have spots", "Sharks don't eat people", "Robins lay eggs", "Robins are female", "Mosquitos carry malaria")))

s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
  #geom_jitter(width = 0.1, shape = 21, size = 5)+
  #ylab("Human endorsement probability")+
  #xlab("Frequency of target")+
  geom_label_repel(data = s1.simulations.relabeled, 
                   aes( label = example, fill = example),
                       color = 'white',
    box.padding = unit(0.0, "lines"),
    #point.padding = unit(1e-06, "lines"),
    segment.color = 'grey37')+
  scale_fill_solarized()+
  scale_x_continuous(limits = c(0, 1), 
                     breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(-0.01, 1.01), 
                     breaks = c(0, 1),
                     labels = c("False", "True"))+
  coord_fixed(ratio = 1)+
  guides(fill = F)+
  ylab("Endorsement model prediction")+
  xlab("Hypothesized feature-probability")

@@

```{r simulations_l0, fig.cap = "Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions. The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions."}
all.simulations.refactored <- all.simulations %>%
  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
  filter(Distribution != "Some", Distribution != "Most") %>%
  mutate(Distribution = factor(Distribution, levels = 
                                c( "Prior_generic", "Posterior_Generalization_generic"),
                                labels = c( "Prior/Silence", "Generalization")
                             # c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
                             #    labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")
                             ),
         PriorShape = factor(PriorShape, 
                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria")
                            # levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
                             #labels = c("uniform", "bark","lay eggs","carry malaria","are female")
                                  #"eatsFood","areSick", "uniformRare", 
                                  #"carriesMalaria"
                                  )
         )

l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
                #lty = Distribution, 
                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
    geom_density(aes(y = ..scaled..),
                 size = 0.6,  adjust = 1.5)+
    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
    theme_few() +
    scale_color_solarized()+
    scale_fill_solarized()+
    scale_alpha_manual(values = c(0.7, 0.3))+
    scale_linetype_manual(values = c(1, 3))+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
   #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Feature-probability h") +
    ylab("Scaled prior probability density") +
  facet_wrap(~PriorShape, scales = 'free')+
  guides(fill = F, color = F)+
  theme(strip.text.y = element_text(angle = 0),
          legend.position = c(0.92, 0.35))
```

```{r simulations, fig.cap = "Model behavior. Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions. The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 14, fig.height=6, cache=F}
grid.arrange(l0.simulations.distributions, 
             s1.simulations.scatter, ncol = 3,
             layout_matrix = cbind(c(1,1), c(1,1), c(2, 2)))

>>>>

```{r libraries, cache = F}
library(papaja)
library(formatR)
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
# library(dplyr)
library(data.table)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
library(gridExtra)
library(lme4)
library(knitr)
library(kableExtra)
library(cowplot)
library(magick)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
logmeanexp <- function(x){
  x.num <- as.numeric(x)
  xstar = max(x.num)
  return(xstar + log(mean(exp(x.num - xstar))))
}

@@

```{r rsaHelpers}
rsaHelpers <- '
var probability = function(Dist, x) {
    return Math.exp(Dist.score(x));
}
var targetUtterance = "generic";

var round = function(x){
  return Math.round(x*1000)/1000
}
var utterancePrior = Infer({model: function(){
  return uniformDraw([targetUtterance,"silence"])
}});

var thetaBins = map(round, _.range(0.01, 0.98, 0.01))
// var thetaBins = [
//    0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
//    0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
 // ]
var thetaPrior = Infer({model: function(){
 return uniformDraw(thetaBins)
}});

var bins = map(round, _.range(0.01, 0.99, 0.01))

// var bins = [
  // 0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
  // 0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
// ];

@@

var statePrior = Infer({model: function(){
  var component = flip(mixture);
  return component ?
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta(priorParams), b) + Number.EPSILON
      }, bins )
    }) :
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
      }, bins )
    })
}});
'
```

```{r rsaInterpretationModels, eval = T, cache = T}
no.utterance.model <- '
var noUtteranceInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    return { state }
 }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
'

fixed.threshold.model <- '
var fixedThresholdInterpreter = function(threshold) {
  Infer({model: function(){
  // var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
  var state = sample(statePrior)
  condition( state > threshold)
    return {
      state: state
  }
 // }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
 }, method: "enumerate"})}
'

uncertain.threshold.model <- '
var uncertainThresholdInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    factor( Math.log(state) )
    return {
      state: state, 
  }
  }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
'

```{r simulationCalls}
fixed.threshold.calls <- '
_.fromPairs(map(function(t){return [t, fixedThresholdInterpreter(t)]}, [0.1, 0.3, 0.5, 0.7, 0.9]))
'
no.utterance.call <- ' 
  noUtteranceInterpreter()
'
uncertain.threshold.call <- '
  uncertainThresholdInterpreter()
'
```

```{r}
priorNames <- c(
  "doesntEatPeople", #"uniformRare", 
  "isFemale", 
  "laysEggs", 
  #"eatsFood", 
  "barks",
  "carriesMalaria",
  "hasSpots"
 # "areSick"
  )
priorShapes <- list(
  isFemale =  list(params = data.frame(a = 10, b = 10), mix = 1), 
  laysEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.4), 
  doesntEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1), 
  barks =  list(params = data.frame(a = 5, b = 1), mix = 0.4), 
  hasSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7), 
  carriesMalaria =  list(params = data.frame(a = 2, b = 10), mix = 0.4)
)

sims.fixed.thresholds <- data.frame()
sims.priors <- data.frame()
sims.uncertain.thresholds <- data.frame()

for (p in priorNames){

  inputData = list(prior = priorShapes[[p]])
  rs.fixed.threshold.model <- webppl(paste(rsaHelpers, fixed.threshold.model, fixed.threshold.calls, sep = '\n'), data = inputData, data_var = "data")
  rs.uncertain.threshold.model <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
  rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")

  sims.fixed.thresholds <- bind_rows(sims.fixed.thresholds,
    bind_rows(
      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.1`) %>% rename(prob = probs), 20000), threshold = 0.1) ,
      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.3`) %>% rename(prob = probs), 20000), threshold = 0.3),
      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.5`) %>% rename(prob = probs), 20000), threshold = 0.5),
      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.7`) %>% rename(prob = probs), 20000), threshold = 0.7),
      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.9`) %>% rename(prob = probs), 20000), threshold = 0.9)
    ) %>% 
      mutate(PriorShape = p)
    )

  sims.uncertain.thresholds <- bind_rows(sims.uncertain.thresholds, rs.uncertain.threshold.model %>% select(value) %>% rename(state = value) %>% mutate(PriorShape = p))
  sims.priors <- bind_rows(sims.priors, rs.prior %>% select(value) %>% rename(state = value) %>% mutate(PriorShape = p))
}
```

```{r cache = F}
fig.sims.priors <- ggplot(sims.priors, aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    ylab("Normalized probability density") +
    xlab("")+
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(PriorShape~., scales = 'free')+
    theme(strip.text.y = element_blank())
```

```{r cache = F}
fig.sims.fixed.thresholds <- ggplot(sims.fixed.thresholds, aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.3)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Feature-probability") +
    ylab("") +
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(PriorShape~threshold, scales = 'free')+
    theme(strip.text.y = element_blank(), axis.title.x = element_text(hjust = 1))
```

```{r cache = F}
fig.sims.uncertain.threshold <- sims.uncertain.thresholds %>% mutate(PriorShape = factor(PriorShape, 
                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria"))) %>% 
                              ggplot(., aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("") +
    ylab("") +
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(PriorShape~., scales = 'free')+
    theme(strip.text.y = element_blank())#element_text(angle = 0, hjust = 0))
```

```{r fig.width = 9, eval = F}
p1 <- fig.sims.priors +
  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("Feature-probability priors")
p2 <- fig.sims.fixed.thresholds +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
p3 <- fig.sims.uncertain.threshold+
  theme(plot.margin = unit(c(18,0,6,6), "pt"))+ 
    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")

prow <- plot_grid( p1 + theme(legend.position="none"),
           p2 + theme(legend.position="none"),
           p3 + theme(legend.position="none"),
           align = 'vh',
           labels = c("A", "B", "C"),
           hjust = -1,
           nrow = 1,
           #rel_widths = c(1.2, 3, 2)
           rel_widths = c(1.2, 3, 1.2)
           )
#prow
#legend <- get_legend(p1)

#plot_grid( prow, legend, rel_widths = c(3, .3))
```

```{r simluationEndorsementModel, eval = T, cache = T}
s1.model <- '
var interpreter = cache(function(utterance) {
  Infer({model: function(){
    var state = sample(statePrior)
    var theta = utterance == "generic" ? sample(thetaPrior) : -99
    condition(meaning(utterance, state, theta))
    return state
 }})}, 10000)

var alpha = 2

var endorser = function(featureProb){
  Infer({model: function(){
    var endorsement = sample(utterancePrior)
    var L0 = interpreter(endorsement)
    factor(alpha * L0.score(featureProb))
    return endorsement
  }})
}
// console.log(data.featureProb[0])
probability(endorser(data.featureProb[0]), "generic")
'

exampleGenerics <- c(
  "sharksDontEatPeople",
  "robinsAreFemale", 
  "robinsLayEggs", 
  "kangaroosHaveSpots",
  "dogsBark",
  "mosquitosCarryMalaria"
  )

exampleParameters <- list(
  robinsAreFemale =  list(prior = list(params = data.frame(a = 10, b = 10), mix = 1), featureProb = 0.5), 
  robinsLayEggs =  list(prior = list(params = data.frame(a = 10, b = 10), mix = 0.2), featureProb = 0.5), 
  sharksDontEatPeople =  list(prior = list(params = data.frame(a = 50, b = 1), mix = 1), featureProb = 0.8), 
  dogsBark =  list(prior = list(params = data.frame(a = 5, b = 1), mix = 0.4), featureProb = 0.9), 
  kangaroosHaveSpots =  list(prior = list(params = data.frame(a = 5, b = 1), mix = 0.7), featureProb = 0.1), 
  mosquitosCarryMalaria =  list(prior = list(params = data.frame(a = 1, b = 30), mix = 0.1), featureProb = 0.1)
)

@@

    s1.rs <- webppl(paste(rsaHelpers, s1.model, sep = "\n"), data = exampleParameters[[p]], data_var = "data")
    s1.simulations <- bind_rows(s1.simulations,
                                   data.frame(example = p, endorsement = s1.rs, featureProb = exampleParameters[[p]]["featureProb"] ))

@@

```{r}
s1.simulations.relabeled <- s1.simulations %>%
  mutate(example = factor(example, 
                          levels = c("dogsBark", "kangaroosHaveSpots", "sharksDontEatPeople", "robinsLayEggs", "robinsAreFemale", "mosquitosCarryMalaria"),
                            labels = 
                            c("Dogs bark", "Kangaroos have spots", "Sharks don't eat people", "Robins lay eggs", "Robins are female", "Mosquitos carry malaria")
                            #c("Dogs", "Kangaroos", "Sharks", "Robins ", "Robins", "Mosquitos")
                          ))

# s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
#   #geom_jitter(width = 0.1, shape = 21, size = 5)+
#   #ylab("Human endorsement probability")+
#   #xlab("Frequency of target")+
#   geom_label_repel(data = s1.simulations.relabeled, 
#                    aes( label = example, fill = example),
#                        color = 'white',
#     box.padding = unit(0.0, "lines"),
#     #point.padding = unit(1e-06, "lines"),
#     segment.color = 'grey37')+
#   scale_fill_solarized()+
#   scale_x_continuous(limits = c(0, 1), 
#                      breaks = c(0, 0.5, 1))+
#   scale_y_continuous(limits = c(-0.01, 1.01), 
#                      breaks = c(0, 1),
#                      labels = c("False", "True"))+
#   coord_fixed(ratio = 1)+
#   guides(fill = F)+
#   ylab("Endorsement model prediction")+
#   xlab("Hypothesized feature-probability")

s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement, fill = example))+
  geom_col(color = 'black')+
  # geom_label_repel(data = s1.simulations.relabeled, 
  #                  aes( label = example, fill = example),
  #                      color = 'white',
  #   box.padding = unit(0.0, "lines"),
  #   #point.padding = unit(1e-06, "lines"),
  #   segment.color = 'grey37')+
  scale_fill_solarized()+
  scale_x_continuous(limits = c(0, 1), 
                     breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(-0.01, 1.01), 
                     breaks = c(0, 1))+
                     #labels = c("False", "True"))+
  coord_fixed(ratio = 1)+
  facet_grid(example~.)+
  guides(fill = F)+
  ylab("Endorsement")+xlab("Referent feature-probability")+
  theme(strip.text.y = element_text(angle = 0, hjust = 0), 
        axis.title.x = element_text(hjust = 0)
        #axis.title.y = element_text(vjust = 0)
        )
  #ylab("Endorsement model prediction")+
  #xlab("Hypothesized feature-probability")
#s1.simulations.scatter
```

```{r simulations, fig.cap = "Computational model behavior. A: Prior distributions over feature-probabilities for 6 example generalizations. B: Different fixed thresholds (columns) give rise to different posterior interpretations. C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors. D: Endorsement model predictions, assuming a particular referent feature-probability. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 12, cache=F}
p1 <- fig.sims.priors +
  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("Feature-probability priors")
p2 <- fig.sims.fixed.thresholds +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
p3 <- fig.sims.uncertain.threshold+
  theme(plot.margin = unit(c(18,0,6,6), "pt"))+ 
    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,0), "pt"))

prow <- plot_grid( p1 + theme(legend.position="none"),
           p2 + theme(legend.position="none"),
           p3 + theme(legend.position="none"),
           p4,
           align = 'vh',
           labels = c("A", "B", "C", "D"),
           hjust = -1,
           nrow = 1,
           #rel_widths = c(1.2, 3, 2)
           rel_widths = c(1.2, 3, 1.1, 3)
           )
prow
```

```{r eval = F}
all.simulations.refactored <- all.simulations %>%
  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
  filter(Distribution != "Some", Distribution != "Most") %>%
  mutate(Distribution = factor(Distribution, levels = 
                                c( "Prior_generic", "Posterior_Generalization_generic"),
                                labels = c( "Prior/Silence", "Generalization")
                             # c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
                             #    labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")
                             ),
         PriorShape = factor(PriorShape, 
                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria")
                            # levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
                             #labels = c("uniform", "bark","lay eggs","carry malaria","are female")
                                  #"eatsFood","areSick", "uniformRare", 
                                  #"carriesMalaria"
                                  )
         )

l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
                #lty = Distribution, 
                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
    geom_density(aes(y = ..scaled..),
                 size = 0.6,  adjust = 1.5)+
    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
    theme_few() +
    scale_color_solarized()+
    scale_fill_solarized()+
    scale_alpha_manual(values = c(0.7, 0.3))+
    scale_linetype_manual(values = c(1, 3))+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
   #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Feature-probability h") +
    ylab("Scaled prior probability density") +
  facet_wrap(~PriorShape, scales = 'free')+
  guides(fill = F, color = F)+
  theme(strip.text.y = element_text(angle = 0),
          legend.position = c(0.92, 0.35))

l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
    geom_density(aes(y = ..scaled..),
                 size = 0.6,  adjust = 1.5)+
    theme_few() +
    scale_color_solarized()+
    scale_fill_solarized()+
    scale_alpha_manual(values = c(0.7, 0.3))+
    scale_linetype_manual(values = c(1, 3))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Feature-probability h") +
    ylab("Scaled prior probability density") +
  facet_wrap(~PriorShape, scales = 'free')+
  guides(fill = F, color = F)+
  theme(strip.text.y = element_text(angle = 0),
          legend.position = c(0.92, 0.35))

@@

```{r simulationsOld, eval = F, fig.cap = "Model behavior. Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions. The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 14, fig.height=6, cache=F}
grid.arrange(l0.simulations.distributions, 
             s1.simulations.scatter, ncol = 3,
             layout_matrix = cbind(c(1,1), c(1,1), c(2, 2)))
